### 2019-07-23 beamer2thesis/dummy.tex
update

\documentclass{scrartcl}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{csquotes}
% Include Graphic-files:
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subfig}
\usepackage{url}
%\usepackage{subfig}
\newsubfloat{figure}
\newcommand{\source}[1]{\vspace{-3pt} \caption*{ Source: {#1}} }

@@

\begin{table}[h]
\scriptsize
\centering
\caption{Challenges in generative modeling:}
\begin{tabularx}{\textwidth}{X|X|X}
Global Illumination Methods & Symmetric Tensor Field Visualization & Asymmetric Tensor Field Visualization\\
\toprule
\begin{itemize}
	\item
\end{itemize}
&
\begin{itemize}
	\item
\end{itemize}
& 
\begin{itemize}
	\item
\end{itemize}
\hline 
\end{tabularx}
   \vskip 1pt
\end{table}

>>>>

\documentclass{beamer}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{csquotes}
% Include Graphic-files:
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subfig}
\usepackage{url}
%\usepackage{subfig}
\newsubfloat{figure}
\newcommand{\source}[1]{\vspace{-3pt} \caption*{ Source: {#1}} }

@@

\frame{
\frametitle{{Introduction - Scalar Fields}}
\begin{columns}
\begin{column}{.5\textwidth}
\begin{itemize}
	\item Scalar fields are visualized by heat maps (color codings) classically
	\bigskip
	\item Each position in space is mapped a scalar height value
	\bigskip
	\item Examples: temperature field, height field
\end{itemize}
\end{column}
\begin{column}{.5\textwidth}
\begin{figure}[t]
\includegraphics[width=0.7\textwidth]{Scalar_field.png} 
\caption{Scalar field,  \textit{Source: \textcircled{1}}}
\end{figure}
\end{column}
\end{columns}

} % END OF FRAME

\frame{
\frametitle{{Introduction - Vector Fields}}
\begin{columns}
\begin{column}{.5\textwidth}
\begin{itemize}
	\item Vector fields are visualized by a collection of arrows with a given magnitude and direction classically
	\bigskip
	\item Each position in space is mapped a scalar magnitude and an angle
	\bigskip
	\item Examples: flow field, magnetic field, gravitational field
\end{itemize}
\end{column}
\begin{column}{.5\textwidth}
\begin{figure}[t]
\includegraphics[width=0.6\textwidth]{vector_field.pdf} a)
\includegraphics[width=0.6\textwidth]{vector_field2.pdf} b)
\caption{Vector fields: a) $\{x,y\}$, b) $\{-y,x\}$}
\end{figure}

\end{column}
\end{columns}

} % END OF FRAME

\frame{
\frametitle{{Introduction - Tensor Fields}}
\begin{columns}
\begin{column}{.5\textwidth}
\begin{itemize}
	\item Tensor fields are commonly visualized by:
	\begin{itemize}
		\item Glyphs
		\item Tensor field lines (TFLs) $\Rightarrow$ Hyperstreamlines
	\end{itemize}
	\bigskip
	\item Each position in space is mapped a tensor describing a directional distribution
	\bigskip
	\item Scalar Measures: anisotropy index, tensor magnitude
\end{itemize}
\end{column}
\begin{column}{.5\textwidth}
\begin{figure}[t]
\includegraphics[width=0.6\textwidth]{hyperstreamlines.png} a)
\includegraphics[width=0.6\textwidth]{random-global.png} b)
\caption{Tensor fields: a) Tensor field lines, b) Glyphs}
\end{figure}

\end{column}
\end{columns}

} % END OF FRAME

\frame{
\frametitle{{Motivation - Tensor Fields}}
Applications:
\begin{itemize}
	\item Vector fields: to describe the directionally dependent spatial gradient called Jacobian-matrix,
	\item Fluid and solid continuum mechanics: to describe a whole distribution of stresses
	\item DT-MRI: diffusion tensor - magnetic resonance imaging: to describe the diffusion characteristics of water molecules within tissue
\end{itemize}
} % END OF FRAME
